A Survey of Fuzzing and New Technique for Dynamic Analysis

### 2014-02-18 docs/paper/fsuthesis/thesis-template/paper.tex
small changes/additions to paper

@@

TODO Peach Fuzzer

@@

@@

	\item [B] DeMott, J., Enbody, R., and Punch, W. "Revolutionizing the Field of Grey-box Attack Surface Testing with
Evolutionary Fuzzing", BlackHat and Defcon 2007.

@@

	\item [E] ... "Beyond Instruction Level Taint Propagation".

@@

>>>>

\subsection{Grey-box Evolutionary Fuzzing}

@@

TODO Peach Fuzzer does both, overview with pictures?

@@

Koushik Sen defines concolic testing as combining "random tesing and symbolic execution to partly remove the limitations of random testing and symbolic execution based testing" [AB]. This differs from hybrid symbolic execution engines like Mayhem [H], which switch between different types of symbolic execution. Hybrid symbolic execution does not itself supplement fuzzing by adding concrete random values. Both imply a tradeoff between two types of analysis, however, and thus both, when implemented by different people, will differ in where they assign the tradeoff. Some concolic testing, for instance, will start with concrete values which are random, or NULLs for pointer values. After an execution, one of the symbolic constraints will be negated, to allow a new path to be explored, and the program will be run again with new random input [AB]. Various research aims to either use symbolic execution less [Q, R, X], pick better than random values [A], or pick better input bytes to give random values [A, E, T, AB].

@@

	\item [B] DeMott, J., Enbody, R., and Punch, W. "Revolutionizing the Field of Grey-box Attack Surface Testing with Evolutionary Fuzzing", BlackHat and Defcon 2007.

@@

	\item [E] Ajit, Beng Heng Ng Earlence Fernandes, Aluri Atul Prakash, and David Rodriguez Velazquez Zijiang Yang. "Beyond Instruction Level Taint Propagation." (2013).

@@

	\item [AC] Sen, Koushik. "Concolic testing." Proceedings of the twenty-second IEEE/ACM international conference on Automated software engineering. ACM, 2007.
